---
title: "Lab 02 - Plastic waste"
author: "Rebecca Smith"
date: "02/08/2021"
output: html_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

```{r dist-per-cap}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)
```
```{r filter_waste_per_cap}
plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)
```
### Exercise 1

Based on these histograms, North America appears to have the most plastic waste per capita whereas South America appears to have the lowest amount of plastic waste per capita.

```{r plastic-waste-continent}
ggplot (data = plastic_waste, aes (x = plastic_waste_per_cap))+
  geom_histogram(binwidth = .25)+
  facet_wrap(~continent)
```

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, color = continent, fill = continent)) + 
  geom_density(alpha = 0.3)

```

### Exercise 3

I changed the alpha level to 0.3.

### Exercise 4

We defined color and fill by mapping aesthetics because because these determinations are made based on variables in the data. We defined alpha as a characteristic of the plotting geom because this determination was not based on the values or variables in the data.

```{r plastic-waste-violin}
ggplot (data = plastic_waste, mapping = aes (x=continent, y = plastic_waste_per_cap)) +
  geom_violin()
```

### Exercise 5

The violin plots display the distributions a bit better. We can clearly see the outliers in this visualization. The different shapes of the violins also allows us to have a better grasp of what the distribution looks like per continent. With the boxplots, we can see how the data is differentiated into quartiles. 

```{r plastic-waste-mismanaged}
ggplot (data = plastic_waste, aes (x = plastic_waste_per_cap, y = mismanaged_plastic_waste_per_cap))+
  geom_point()
```

### Exercise 6

The scatterplot shows a moderately positive relationship between plastic waste per capita and mismanaged plastic waste per capita. That is, the more plastic waste there is, the more mismanaged the waste becomes.

```{r plastic-waste-mismanaged-continent}
ggplot (data = plastic_waste, aes (x = plastic_waste_per_cap, y = mismanaged_plastic_waste_per_cap, color = continent)) +
  geom_point()
```

### Exercise 7

The two clearest distinctions are the outliers for Asia and Oceania. However, even with the most plastic waste, Oceania's mismanagement of it is less than that of Asia. 

```{r plastic-waste-population-total}
ggplot (data = plastic_waste, aes (x = total_pop, y = plastic_waste_per_cap, color = continent) ) +
  geom_point()
```

```{r plastic-waste-population-coastal}
ggplot (data = plastic_waste, aes (x = coastal_pop, y = plastic_waste_per_cap, color = continent)) +
  geom_point()
```

### Exercise 8

The relationship between coastal population and plastic waste per capita appears to be more strongly linearly associated. 

```{r recreate-viz}
ggplot (data = plastic_waste, aes (x = coastal_pop / total_pop, y = plastic_waste_per_cap, color = continent))+
  geom_point()+
  stat_smooth()
```
This is as close as I could get to the visualization of plastic waste vs. coastal population proportion. It would appear that, as the coastal population reaches the same amount as the total population (in terms of the proportion), there is the most plastic waste per capita. 