---
title: "Lab 02 - Plastic waste"
author: "Rebecca Smith"
date: "02/08/2021"
output: html_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

```{r dist-per-cap}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)
```
```{r filter_waste_per_cap}
plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)
```
### Exercise 1

Based on these histograms, North America appears to have the most plastic waste per capita whereas South America appears to have the lowest amount of plastic waste per capita.

```{r plastic-waste-continent}
ggplot (data = plastic_waste, aes (x = plastic_waste_per_cap))+
  geom_histogram(binwidth = .25)+
  facet_wrap(~continent)
```

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, color = continent, fill = continent)) + 
  geom_density(alpha = 0.3)

```

### Exercise 3

I changed the alpha level to 0.3.

### Exercise 4

We defined color and fill by mapping aesthetics because we wanted to adjust the way that the continents were displayed on the graph. We defined alpha as a characteristic of the plotting geom because we wanted to adjust the overall display of the histogram.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
